Watch Out for the Bully! Job Interference Study on Dragonfly Network

### 2016-03-20 draft.tex
add a few missing word
add figs with hybrid placement

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Watch Out for the Bully! Study of Interference Between Jobs Running Concurrently on Dragonfly Network}

@@

In this work we simulate and analyze six combinations of placement policies and routing schemes, which are summarized in Table ref{tab: placement routing configs}. Our analysis focuses on both overall network workload and individual application performance. For overall workload analysis, we focus on the time spent on communication by the workload, the network traffic throughput and busy time of links and channels. For individual application analysis, we study the time spent on communication by each MPI rank, traffic and busy time of each router that belongs to specific application. In our experiments, we collect and analyze the following data:

@@

With respect to random placement, we conduct a number of random runs, which are used to eliminate the possibility of variation.

@@

\section{Study of Parallel Workload \Rmnum{1 }}
\label{sec:workload-1}

@@

\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{amg/commtime}
        \caption{AMG Communication Time}
        \label{fig:amg-commtime}
    \end{subfigure}%
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{mg/commtime}
        \caption{MG Communication Time}
        \label{fig:mg-commtime}
    \end{subfigure}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{cr/commtime}
        \caption{CR Communication Time}
        \label{fig:cr-commtime}
    \end{subfigure}%
   \caption{Application communication time. Three applications running concurrently on dragonfly network with different placement and routing configurations. Random placement and adaptive routing can improve MG and CR communication, however, AMG's communication time is greatly prolonged.}
   \label{fig:apps-commtime}
\end{figure*}

@@

\begin{figure*}[t]
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{amg/lc-traffic}
        \caption{AMG Local Channel Traffic}
        \label{fig:amg-lc-traffic}
    \end{subfigure}\hfill
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{mg/lc-traffic}
        \caption{MG Local Channel Traffic}
        \label{fig:mg-lc-traffic}
    \end{subfigure}\hfill
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{cr/lc-traffic}
        \caption{CR Local Channel Traffic}
        \label{fig:cr-lc-traffic}
    \end{subfigure}\\

    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{amg/gc-traffic}
        \caption{AMG Global Channel Traffic}
        \label{fig:amg-gc-traffic}
    \end{subfigure}\hfill
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{mg/gc-traffic}
        \caption{MG Global Channel Traffic}
        \label{fig:mg-gc-traffic}
    \end{subfigure}\hfill
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{cr/gc-traffic}
        \caption{CR Global Channel Traffic}
        \label{fig:cr-gc-traffic}
    \end{subfigure}%
   \caption{The traffic go through the local and global channels of routers that belongs to specific application.}
   \label{fig:3app-lc-gc-traffic}
\end{figure*}

@@

\emph{Random placement \& adaptive routing is quite efficient for orchestrate the traffic load in the network by uniformly distributing the workload traffic all over the network. However, application like AMG will be impaired in this orchestration. The routers through which the less communication-intensive application traffic used to route, now have more traffic go through them. These extra traffic are from other communication-intensive applications. Beneath the facade of harmony, less communication-intensive application are ``bullied" by their concurrently running communication-intensive peers in the workload. }

\emph{Random placement \& adaptive routing can not guarantee QoS for each application in the workload. In order to reach load-balanced and hot-spots free, the traffic from congested routers will be redirected to other less busy routers. This will indulge the ``bully" that communication-intensive applications impose to their less intensive peers.}

@@

\section{Parallel Workload \Rmnum{2 }}
\label{sec:workload-2}

@@

\begin{figure*}[t]
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/amg10/lc-traffic}
        \caption{sAMG Local Channel Traffic}
        \label{fig:syn-samg-lc-traffic}
    \end{subfigure}\hfill
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/mg/lc-traffic}
        \caption{MG Local Channel Traffic}
        \label{fig:syn-mg-lc-traffic}
    \end{subfigure}\hfill
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/cr/lc-traffic}
        \caption{CR Local Channel Traffic}
        \label{fig:syn-cr-lc-traffic}
    \end{subfigure}\\
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/amg10/gc-traffic}
        \caption{sAMG Global Channel Traffic}
        \label{fig:syn-samg-gc-traffic}
    \end{subfigure}\hfill
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/mg/gc-traffic}
        \caption{MG Global Channel Traffic}
        \label{fig:syn-mg-gc-traffic}
    \end{subfigure}\hfill
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/cr/gc-traffic}
        \caption{CR Global Channel Traffic}
        \label{fig:syn-cr-gc-traffic}
    \end{subfigure}%
   \caption{Each Application Router Local and Global Channel Traffic.}
   \label{fig:syn-3app-gc-traffic}
\end{figure*}

@@

\emph{Second, there are variance in terms of communication intensity between concurrently running applications. In workload \Rmnum{1}, AMG has the least amount of communication traffic compared with MultiGrid and CrystalRouter and it become the ``bullee". In workload \Rmnum{2}, sAMG has the most amount of communication traffic, which makes it the ``bully". }

We can stop this ``bully" by making either one of these conditions invalid.

>>>>

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Watch Out for the Bully! Job Interference Study on Dragonfly Network}

@@

In this work we simulate and analyze six combinations of placement policies and routing schemes, which are summarized in Table \ref{tab: placement routing configs}. Our analysis focuses on both overall network workload and individual application performance. For overall workload analysis, we focus on the time spent on communication by the workload, the network traffic throughput and busy time of links and channels. For individual application analysis, we study the time spent on communication by each MPI rank, traffic and busy time of each router that belongs to specific application. In our experiments, we collect and analyze the following data:

@@

With respect to random placement, we conduct our experiment with a set of distinctive random allocation, which are intended to eliminate the possibility of variation.

@@

% \section{Study of Parallel Workload \Rmnum{1 }}
\section{Identify the ``Bully"}
\label{sec:workload-1}

@@

\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{wkld/amg/commtime}
        \caption{AMG Communication Time}
        \label{fig:amg-commtime}
    \end{subfigure}%
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{wkld/mg/commtime}
        \caption{MG Communication Time}
        \label{fig:mg-commtime}
    \end{subfigure}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{wkld/cr/commtime}
        \caption{CR Communication Time}
        \label{fig:cr-commtime}
    \end{subfigure}%
   \caption{Application communication time. Three applications running concurrently on dragonfly network with different placement and routing configurations. Random placement and adaptive routing can improve MG and CR communication, however, AMG's communication time is greatly prolonged.}
   \label{fig:apps-commtime}
\end{figure*}

@@

\begin{figure*}[t]
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{wkld/amg/lc-traffic}
        \caption{AMG Local Channel Traffic}
        \label{fig:amg-lc-traffic}
    \end{subfigure}\hfill
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{wkld/mg/lc-traffic}
        \caption{MG Local Channel Traffic}
        \label{fig:mg-lc-traffic}
    \end{subfigure}\hfill
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{wkld/cr/lc-traffic}
        \caption{CR Local Channel Traffic}
        \label{fig:cr-lc-traffic}
    \end{subfigure}\\

    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{wkld/amg/gc-traffic}
        \caption{AMG Global Channel Traffic}
        \label{fig:amg-gc-traffic}
    \end{subfigure}\hfill
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{wkld/mg/gc-traffic}
        \caption{MG Global Channel Traffic}
        \label{fig:mg-gc-traffic}
    \end{subfigure}\hfill
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{wkld/cr/gc-traffic}
        \caption{CR Global Channel Traffic}
        \label{fig:cr-gc-traffic}
    \end{subfigure}%
   \caption{The traffic go through the local and global channels of routers that belong to specific application.}
   \label{fig:3app-lc-gc-traffic}
\end{figure*}

@@

\emph{Random placement \& adaptive routing is quite efficient for orchestrating the traffic load in the network by uniformly distributing the workload traffic all over the network. However, application like AMG will be impaired in this orchestration. Beneath the facade of harmony, less communication-intensive application are ``bullied" by their concurrently running communication-intensive peers in the workload. }

% The routers through which the less communication-intensive application traffic used to route, now have more traffic go through them. These extra traffic are from other communication-intensive applications.

\emph{Random placement \& adaptive routing can not guarantee the qualify of service for each application in the workload. In order to reach load-balanced and hot-spots free over the whole network, the traffic from congested routers will be redirected to other less busy routers. This will indulge the ``bully" that communication-intensive applications impose to their less intensive peers.}

@@

% \section{Parallel Workload \Rmnum{2 }}
\section{``Bully" become ``Bullee"}
\label{sec:workload-2}

@@

\begin{figure*}[t]
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/amg10/lc-traffic}
        \caption{sAMG Local Channel Traffic}
        \label{fig:syn-samg-lc-traffic}
    \end{subfigure}\hfill
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/mg/lc-traffic}
        \caption{MG Local Channel Traffic}
        \label{fig:syn-mg-lc-traffic}
    \end{subfigure}\hfill
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/cr/lc-traffic}
        \caption{CR Local Channel Traffic}
        \label{fig:syn-cr-lc-traffic}
    \end{subfigure}\\
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/amg10/gc-traffic}
        \caption{sAMG Global Channel Traffic}
        \label{fig:syn-samg-gc-traffic}
    \end{subfigure}\hfill
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/mg/gc-traffic}
        \caption{MG Global Channel Traffic}
        \label{fig:syn-mg-gc-traffic}
    \end{subfigure}\hfill
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/cr/gc-traffic}
        \caption{CR Global Channel Traffic}
        \label{fig:syn-cr-gc-traffic}
    \end{subfigure}%
   \caption{The traffic go through the local and global channels of routers that belong to specific application.}
   \label{fig:syn-3app-gc-traffic}
\end{figure*}

@@

\emph{Second, there are difference in terms of communication intensity between concurrently running applications. In workload \Rmnum{1}, AMG has the least amount of communication traffic compared with MultiGrid and CrystalRouter and it become the ``bullee". In workload \Rmnum{2}, sAMG has the most amount of communication traffic, which makes it the ``bully". }

We can stop this ``bully" by making both conditions invalid.

\section{Stop the ``Bully"}

The solution for preventing this ``bully" behavior is to avoid network sharing between concurrently running jobs. Using contiguous placement\& minimal routing could be a way avoid network sharing, but both the workload and network performance could suffer degradation due to local congestion. It is also unrealistic to use different routing scheme for each application with regard to its communication intensity, since routing scheme is pre-configured in the system and can not be changed on the fly. However, the job placement can be versatile to assign different allocation (contiguous or random) to specific application.

Thus, we propose the hybrid placement as a reconcile solution. In the hybrid placement, the less communication-intensive application will get contiguous allocation while the communication-intensive ones will get random allocation. We evaluate the performance of hybrid placement\&routing configurations with parallel Workload \Rmnum{1}. AMG gets contiguous allocation, MultiGrid and CrystalRouter get random allocation.

Figure \ref{fig:hyb-plcmt-apps-commtime} shows each application communication time when hybrid placement coupled with different routing, together with other configurations. As we see from Figure \ref{fig:hyb-plcmt-amg-commtime},

\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.3 in]{hyb-plcmt/amg/commtime}
        \caption{AMG Communication Time}
        \label{fig:hyb-plcmt-amg-commtime}
    \end{subfigure}\hfill
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.3 in]{hyb-plcmt/mg/commtime}
        \caption{MG Communication Time}
        \label{fig:hyb-plcmt-mg-commtime}
    \end{subfigure}\hfill
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.3 in]{hyb-plcmt/cr/commtime}
        \caption{CR Communication Time}
        \label{fig:hyb-plcmt-cr-commtime}
    \end{subfigure}%
   \caption{Application communication time. Three applications running concurrently on dragonfly network with different placement\& routing configurations. }
   \label{fig:hyb-plcmt-apps-commtime}
\end{figure*}
